\documentclass[letterpaper,onecolumn,10pt]{article}
\pagestyle{empty}
\usepackage[hmargin=0.6in,vmargin=0.7in]{geometry}   %%Config the content location in the letters.
\usepackage{url}

\begin{document}
\date{}
\title{\fontsize{14}{0}\selectfont \bf Changming Liu}
\author{\fontsize{13}{0}\selectfont\ PhD Candidate, Northeastern University, Boston, MA}
\maketitle
\thispagestyle{empty}
\section*{\fontsize{13}{0}\selectfont Contact Information \\ \rule[-7pt]{1\textwidth}{1pt}}
\textbf{Google Scholar: }https://scholar.google.com/citations?user=DBc2YBoAAAAJ
\hfill
\textbf{Phone: }+1-617-637-6223\\
\raggedright
\textbf{Github: }https://github.com/Lawliar
\hfill
\textbf{Email: } charley.ashbringer@gmail.com\\
\raggedright



\section*{\fontsize{13}{0}\selectfont Education \\ \rule[-7pt]{1\textwidth}{1pt}}

{\bf Northeastern University}
\hspace*{\fill}
Boston, USA \\
PhD student of Cybersecurity in Khoury College of Computer Science
\hspace*{\fill}
Sept 2019 - Now \\
Advised by Prof Long Lu and Prof Engin Kirda

\bigbreak

{\bf Huazhong University of Sci \& Tech}
\hspace*{\fill}
Wuhan, China \\
M.Eng student of Computer Architecture in School of Computer Sci \& Tech
\hspace*{\fill}
Sept 2016 - June 2019 \\
Advised by Prof Hai Jin

\bigbreak

{\bf Huazhong University of Sci \& Tech}
\hspace*{\fill}
Wuhan, China \\
B.Eng student of Information Security in School of Computer Sci \& Tech
\hspace*{\fill}
Sept 2012 - June 2016 \\
Advised by Prof Deqing Zou

\section*{\fontsize{13}{0}\selectfont Publications \\ \rule[-7pt]{1\textwidth}{1pt}}

\begin{itemize}
	\item Zhichuang Sun, Runmin Sun, \underline{Changming Liu}, Chowdhury Amrita Roy, Somesh Jha. 2022. {\bf ShadowNet: A Secure and Efficient System for On-device Model Inference}. Oakland 2023 to appear, https://arxiv.org/abs/2011.05905. 
\end{itemize}
\begin{itemize}
	\item \underline{Changming Liu}, Xiaojing Ma, Sixing Cao, Jiayun Fu, and Bin B. Zhu. 2022. {\bf Privacy-preserving Motion Detection for HEVC-compressed Surveillance Video}. 
	ACM Trans. Multimedia Comput. Commun. Appl. 18, 1, Article 23 (January 2022), 27 pages.
\end{itemize}
\begin{itemize}
	\item \underline{Changming Liu}, Yaohui Chen, and Long Lu. 2021. {\bf KUBO: Precise and Scalable Detection of User-triggerable Undefined Behavior Bugs in OS Kernel}. 
	In Proceedings of the 28th Network and Distributed System Security Symposium(NDSS 2021), Virtual Conference, 21st February - 25th February 2021.
\end{itemize}
\begin{itemize}
	\item Peng Luo, Deqing Zou, Yajuan Du, Hai Jin, \underline{Changming Liu}, and Jinan Shen. 2020. {\bf Static detection of real-world buffer overflow induced by loop}. Computers \& Security, Volume 89, 2020, 101616, ISSN 0167-4048.
\end{itemize}
\begin{itemize}
	\item \underline{Changming Liu}, Deqing Zou, Peng Luo, Bin B. Zhu, and Hai Jin. 2018. {\bf A Heuristic Framework to Detect Concurrency Vulnerabilities}. In Proceedings of the 34th Annual Computer Security Applications Conference (ACSAC '18). Association for Computing Machinery, New York, NY, USA, 529–541 
\end{itemize}
\begin{itemize}
	\item Xiaojing Ma, \underline{Changming Liu}, Sixing Cao, and Bin B. Zhu. 2018.  {\bf JPEG Decompression in the Homomorphic Encryption Domain}. In Proceedings of the 26th ACM international conference on Multimedia (MM '18). Association for Computing Machinery, New York, NY, USA, 905–913.
\end{itemize}
\begin{itemize}
	\item \underline{Liu Changming}, Fu Cai, Xu Deliang, Sun Lin, Han Lansheng. 2015. {\bf An Energy-Balanced WSN Algorithm Based on Active Hibernation and Data Recovery}. 
	In Proceedings of Algorithms and Architectures for Parallel Processing. ICA3PP 2015. Lecture Notes in Computer Science, vol 9528. Springer, Cham.
\end{itemize}

\section*{\fontsize{11}{0}\selectfont Under submission}
\begin{itemize}
	\item \underline{Changming Liu}, Alejandro Mera, Engin Kirda, Long Lu.  {\bf SPEAR: On-device Symbolic Execution for Embedded Applications}. 
\end{itemize}

\begin{itemize}
	\item Alejandro Mera, \underline{Changming Liu}, Engin Kirda, Long Lu  {\bf SHiFT: Semi-hosted Fuzz Testing for Embedded Applications}. 
\end{itemize}





\section*{\fontsize{13}{0}\selectfont Experience  \\ \rule[-7pt]{1\textwidth}{1pt}}
\raggedright
{\bf Research Assistant }
\hfill
Advisor: Prof. Long Lu and Prof Engin Kirda \hspace{0.3cm} Sept 2019 - Now\\
\raggedright
Khoury College of Computer Science, Northeastern University, Boston MA, USA

\bigbreak

\raggedright
{\bf Research Intern }
\hfill
Mentor: Dr. Kapil Singh \hspace{0.3cm} May 2021 - Aug 2021\\
\raggedright
T.J. Watson Research Center, IBM Information Security Research, Yorktown Heights, NY, USA \\
-\space\space\space\space Building infrastructure for cloud services to establish trust.

\bigbreak

\raggedright
{\bf Research Intern }
\hfill
Mentor: Dr. Bin.B.Zhu \hspace{0.3cm} Sept 2018 - March 2019\\
\raggedright
Software analytics group, Microsoft Research Asia, Beijing, China \\
-\space\space\space\space Designing and implementing scalable fuzzing approach for concurrency bugs.

\bigbreak

\raggedright
{\bf Research Intern }
\hfill
Mentor: Dr. Bin.B.Zhu \hspace{0.3cm} Sept 2018 - March 2019\\
\raggedright
Software analytics group, Microsoft Research Asia, Beijing, China \\
-\space\space\space\space Integrating deep learning-based object detection framework into outlook's anti-phishing system.

\bigbreak
\raggedright
{\bf Research Assistant }
\hfill
Advisor: Prof. S.M.Yiu \hspace{0.3cm} July 2015 - Sept 2015\\
\raggedright
Computer Science Department, University of Hong Kong, Hong Kong, China \\
-\space\space\space\space Research paper reading and implementation about privacy-preserving genome applications.

\section*{\fontsize{13}{0}\selectfont Honors \& Awards  \\ \rule[-7pt]{1\textwidth}{1pt}}
Excellent Intern Award(Top 20\%) \hfill Microsoft Research Asia, 2019 \\
National Scholarship \hfill Ministry of Education of China, 2018 \\
Excellent Intern Award(Top 20\%)\hfill Microsoft Research Asia, 2018 \\
Graduate with honor\hfill Huazhong University of Sci \& Tech, 2016 \\
Merit Student\hfill Huazhong University of Sci \& Tech, 2015 \\
National Scholarship\hfill Ministry of Education of China, 2015 \\


\section*{\fontsize{13}{0}\selectfont Misc  \\ \rule[-7pt]{1\textwidth}{1pt}}
\begin{tabbing}
   \hspace{1.3in}\= \hspace{1.5in}\= \kill % set up two tab positions
    {\bf Talks:} \> Presentation in ACM MM'18; Talk in Korea University(Oct, 2018)\\
    {\bf Programming:} \>Python(practiced);C/C++(practiced);Ocaml(familiar);Java(Basic);\\
	{\bf Hobbies:} \>Badminton and violin. \\
	{\bf Bug Hunt:} \> Find 14 new undefined behaviors bugs in the Linux kernel that are either acknowledged or patched.
\end{tabbing}
\end{document}
